HTW EXAM Fits and Transfer Predictions

### 2023-11-11 Manuscript/manuscript2.qmd
quarto profiles and markdown workflow

```{r}
#| label: tbl-e1-test-nf-deviation
#| tbl-cap: "Testing Deviation - Empirical Summary"
#| tbl-subcap:
#|   - "Full datasets"
#|   - "Intersection of samples with all labels available"

@@

```{r}
library(gt)
```

```{r}
#| label: tbl-example2bbb
#| tbl-cap: "Example"
#| tbl-subcap: 
#|   - "Cars2bb"
#|   - "Pressure2bb"
#| echo: fenced
library(knitr)
kable(head(cars))
kable(head(pressure))
```

>>>>

```{r}
#| label: tbl-e1-test-nf-deviation
#| tbl-cap: "Testing Deviation - Empirical Summary"
#| tbl-subcap:
#|   - "Full datasets"
#|   - "Intersection of samples with all labels available"
#| eval: false

@@

```{r}
# library(gt)
```

```{r}
#| label: tbl-example2bbb
#| tbl-cap: "Example"
#| tbl-subcap: 
#|   - "Cars2bb"
#|   - "Pressure2bb"
#| echo: fenced
# library(knitr)
# kable(head(cars))
# kable(head(pressure))
```

### 2023-11-11 _working/htw_exam.qmd
quarto profiles and markdown workflow

@@

```{r}
#| label: fig-alm-diagram
#| fig.cap: The basic structure of the ALM model.

pacman::p_load(tidyverse,ggplot2,igraph,ggraph)

@@

ggplot() + 
  geom_rect(data = odf, 
            aes(xmin = xmin, xmax = xmax, ymin = ymin, ymax = ymax, fill = type), alpha = 0.2) +
  annotate("text", x = odf$x[odf$type == "Input"], y = odf$y[odf$type == "Input"], 
           label = lab, parse = TRUE, size = 3) +
  geom_text(data = odf %>% filter(type != "Input"), 
            aes(x = x, y = y, label = label), size = 3, fontface="bold") +
  geom_path(data = plot_edges, aes(x = x, y = y, group = id, alpha = weight), alpha=.2) +
  theme_void() +
  theme(legend.position = "none")

```

@@

@deloshExtrapolationSineQua1997 introduced the associative learning model (ALM), a connectionist model within the popular class of radial-basis networks. ALM was inspired by, and closely resembles Kruschke's influential ALCOVE model of categorization [@kruschkeALCOVEExemplarbasedConnectionist1992].

@@

{{< pagebreak >}}

## Model Table
### ALM Activation & Response
| Step | Equation | Description |
|------|----------|-------------|
| **ALM Activation & Response**  |           |
| Input Activation | $a_i(X) = \frac{e^{-c(X-X_i)^2}}{\sum_{k=1}^M e^{-c(X-X_k)^2}}$ | Activation of each input node $X_i$, is a function of the Gaussian similarity between the node value and stimulus X.  |
| Output Activation                 | $O_j(X) = \sum_{k=1}^M w_{ji} \cdot a_i(X)$ | Activation of each Output unit $O_j$ is the weighted sum of the input activations and association weights.   |
| Output Probability                | $P[Y_j|X] = \frac{O_j(X)}{\sum_{k=1}^M O_k(X)}$ | Each output node has associated response, $Y_j$. The probability of response $Y_j$ is determined by the ratio of output activations.  |
| Mean Output                       | $m(x) = \sum_{j=1}^L Y_j \cdot \frac{O_j(x)}{\sum_{k=1}^M O_k(X)}$   | The response to stimulus x is the weighted average of the response probabilities. |
| **ALM Learning**                  |                                                                                                                                                          |
| Feedback Activation               | $f_j(Z) = e^{-c(Z-Y_j)^2}$                  | After responding, feedback signal Z is presented, activating each output node via the Gaussian similarity to the ideal response. |
| Update Weights                    | $w_{ji}(t + 1) = w_{ji}(t) + \alpha \cdot (f_j(Z(t)) - O_j(X(t)) \cdot a_i(X(t))$    | Delta rule to update weights. Magnitude of weight changes controlled by learning rate parameter alpha.  |  
| **EXAM**                          |                                                                                                                                                          |
| Extrapolation                     | $P[X_i|X] = \frac{a_i(X)}{\sum_{k=1}^M a_k(X)}$ | Novel test stimulus X activates input nodes associated with trained stimuli.     |
|                                   | $E[Y|X_i] = m(X_i) + \frac{m(X_{i+1})-m(X_{i-1})}{X_{i+1}-X_{i-1}} \cdot [X - X_i]$ | Slope value computed from nearest training instances and then added to the response associated with the nearest training instance,m(x)    |

{{< pagebreak >}}

@@

Following the procedure used by @mcdanielPredictingTransferPerformance2009, we will assess the ability of both ALM and EXAM to account for the empirical data when fitting the models to 1) only the training data, and 2) both training and testing data. Models will be fit directly to the trial by trial data of each individual participants, both by minimizing the root-mean squared deviation (RMSE), and by maximizing log likelihood. Because ALM has been shown to do poorly at accounting for human patterns extrapolation [@deloshExtrapolationSineQua1997], we will also fit the extended EXAM version of the model, which operates identically to ALM during training, but includes a linear extrapolation mechanism for generating novel responses during testing.

```{r}

almParamsV <- cbind(Model="ALM Test Only",pluck(a_te_v, "Fit"), pluck(a_te_v, "test") %>% summarise(Test_RMSE=RMSE(y,pred)) ) |>
  rbind(cbind(Model="ALM Test & Train", pluck(a_tetr_v,"Fit"), pluck(a_tetr_v, "test") %>% summarise(Test_RMSE=RMSE(y,pred)))) |>
  rbind(cbind(Model="ALM Train Only", pluck(a_tr_v, "Fit"), pluck(a_tr_v, "test") %>% summarise(Test_RMSE=RMSE(y,pred)))) |>
  mutate(across(where(is.numeric), \(x) round(x, 3)))

@@

hybridParamsC <-cbind(Model="Hybrid Test Only",pluck(hybrid_te_c, "Fit"), pluck(hybrid_te_c, "test") %>% summarise(Test_RMSE=RMSE(y,pred))) |>
  rbind(cbind(Model="Hybrid Test & Train", pluck(hybrid_tetr_c,"Fit"), pluck(hybrid_tetr_c, "test") %>% summarise(Test_RMSE=RMSE(y,pred)))) |>
  rbind(cbind(Model="Hybrid Train Only", pluck(hybrid_tr_c, "Fit"), pluck(hybrid_tr_c, "test") %>% summarise(Test_RMSE=RMSE(y,pred)))) |>
  mutate(across(where(is.numeric), \(x) round(x, 3)))

```

```{r}
#| label: tbl-e1-model-fits2V
#| tbl-cap: Varied Group - Fit Parameters and Model RMSE

pander(almParamsV, caption="ALM"); pander(examParamsV, caption="EXAM"); pander(hybridParamsV,caption="Hybrid") 
```

```{r}
#| label: tbl-e1-model-fitsC
#| tbl-cap: Constant Group - Fit Parameters and Model RMSE

pander(almParamsC, caption="ALM"); pander(examParamsC, caption="EXAM"); pander(hybridParamsC,caption="Hybrid")
```

## Varied Testing Predictions
```{r}
#| label: fig-model-preds-varied
#| fig-cap: Varied Group - Mean Model predictions vs. observations
#| fig-height: 12
#| fig-width: 14
#| column: screen-inset-right

####

@@

vte/vtetr/vtr

```

## Varied Testing
```{r fig.height=11, fig.width=11}
#| label: tbl-e1-predsV
#| tbl-cap: Varied group - mean model predictions vs. observations
#| 
tvte<- pluck(a_te_v, "test") |> rename(ALM=pred,Observed=y) %>% 
  cbind(.,EXAM=pluck(ex_te_v, "test") |> pull(pred)) %>%
  cbind(., Hybrid=pluck(hybrid_te_v, "test") |> pull(pred))

@@

pander(tvte, caption="Varied fit to test only")
pander(tvtetr,caption="Varied fit to train and test")
pander(tvtr,caption="Varied fit to train only")

```

## Constant Testing Predictions
```{r}
#| label: fig-model-preds-constant
#| fig-cap: Constant Group - Mean Model predictions vs. observations
#| fig-height: 12
#| fig-width: 14
#| column: screen-inset-right

####

@@

cte/ctetr/ctr

```

```{r}
#| label: tbl-e1-predsC
#| tbl-cap: Constant group - mean model predictions vs. observations
#| 
tcte<- pluck(a_te_c, "test") |> rename(ALM=pred,Observed=y) %>% 
  cbind(.,EXAM=pluck(ex0_te_c, "test") |> pull(pred)) %>%
  cbind(., Hybrid=pluck(hybrid_te_c, "test") |> pull(pred))

@@

pander(tcte, caption="Constant fit to test only")
pander(tctetr,caption="Constant fit to train and test")
pander(tctr,caption="Constant fit to train only")

```

```{r}
#| eval: false
pluck(a_te_v, "train") |> pivot_longer(y:almResp, names_to="Resp", values_to = "vx") |> 
  mutate(dev=x-vx,abs_dev=abs(x-vx)) |>
  learn_curve_plot(tr, vx, Resp,facet_var=x, groupVec=Resp,nbins=8)

@@

list(a_tr_v, a_te_v,a_tetr_v) |> map( ~{pluck(.x, "train") |> pivot_longer(y:almResp, names_to="Resp", values_to = "vx") |> mutate(dev=x-vx,abs_dev=abs(x-vx)) |>
  ungroup() %>%
  gather(key = "variable", value = "y_value", dev, abs_dev, vx) %>%
  group_by(variable) %>%
  group_map(~ learn_curve_plot(.x, x_var = tr, y_var = y_value, color_var = Resp, facet_var = x, groupVec = Resp, nbins = 8, y_label = .y$variable), .keep = TRUE) })

```

# EXAM fit learning curves
```{r}
#| eval: false
pluck(ex_te_v, "train") |> pivot_longer(y:almResp, names_to="Resp", values_to = "vx") |> 
  mutate(dev=x-vx,abs_dev=abs(x-vx)) |>
  learn_curve_plot(tr, vx, Resp,facet_var=x, groupVec=Resp,nbins=8)

pluck(ex_te_v, "train") |> pivot_longer(y:almResp, names_to="Resp", values_to = "vx") |> 
  mutate(dev=x-vx,abs_dev=abs(x-vx)) |>
  ungroup() %>%
  gather(key = "variable", value = "y_value", dev, abs_dev, vx) %>%
  group_by(variable) %>%
  group_map(~ learn_curve_plot(.x, x_var = tr, y_var = y_value, color_var = Resp, facet_var = x, groupVec = Resp, nbins = 8, y_label = .y$variable), .keep = TRUE)

```

```{r}
#| eval: false

optimize_params_weighted_individual <- function(ds, c_values, lr_values, weight_exam_values, input.layer, output.layer) {
    all_results <- list()

@@

>>>>

<details class="code-fold">

<summary>Code</summary>

@@

</details>

<details class="code-fold">

<summary>Code</summary>

```{r}
pacman::p_load(tidyverse,ggplot2,igraph,ggraph)

@@

ggplot() + 
  geom_rect(data = odf, 
            aes(xmin = xmin, xmax = xmax, ymin = ymin, ymax = ymax, fill = type), alpha = 0.2) +
  annotate("text", x = odf$x[odf$type == "Input"], y = odf$y[odf$type == "Input"], 
           label = lab, parse = TRUE, size = 3) +
  geom_text(data = odf %>% filter(type != "Input"), 
            aes(x = x, y = y, label = label), size = 3, fontface="bold") +
  geom_path(data = plot_edges, aes(x = x, y = y, group = id, alpha = weight), alpha=.2) +
  theme_void() +
  theme(legend.position = "none")
```

</details>

![](htw_exam.markdown_strict_files/figure-markdown_strict/fig-alm-diagram-1.jpeg)

@@

DeLosh et al. (1997) introduced the associative learning model (ALM), a connectionist model within the popular class of radial-basis networks. ALM was inspired by, and closely resembles Kruschke's influential ALCOVE model of categorization (Kruschke, 1992).

@@

## Model Table

### ALM Activation & Response

| Step                          | Equation                                                                            | Description                                                                                                                            |
|------------------|------------------------|-------------------------------|
| **ALM Activation & Response** |                                                                                     |                                                                                                                                        |
| Input Activation              | $a_i(X) = \frac{e^{-c(X-X_i)^2}}{\sum_{k=1}^M e^{-c(X-X_k)^2}}$                     | Activation of each input node $X_i$, is a function of the Gaussian similarity between the node value and stimulus X.                   |
| Output Activation             | $O_j(X) = \sum_{k=1}^M w_{ji} \cdot a_i(X)$                                         | Activation of each Output unit $O_j$ is the weighted sum of the input activations and association weights.                             |
| Output Probability            | $P[Y_j|X] = \frac{O_j(X)}{\sum_{k=1}^M O_k(X)}$                                     | Each output node has associated response, $Y_j$. The probability of response $Y_j$ is determined by the ratio of output activations.   |
| Mean Output                   | $m(x) = \sum_{j=1}^L Y_j \cdot \frac{O_j(x)}{\sum_{k=1}^M O_k(X)}$                  | The response to stimulus x is the weighted average of the response probabilities.                                                      |
| **ALM Learning**              |                                                                                     |                                                                                                                                        |
| Feedback Activation           | $f_j(Z) = e^{-c(Z-Y_j)^2}$                                                          | After responding, feedback signal Z is presented, activating each output node via the Gaussian similarity to the ideal response.       |
| Update Weights                | $w_{ji}(t + 1) = w_{ji}(t) + \alpha \cdot (f_j(Z(t)) - O_j(X(t)) \cdot a_i(X(t))$   | Delta rule to update weights. Magnitude of weight changes controlled by learning rate parameter alpha.                                 |
| **EXAM**                      |                                                                                     |                                                                                                                                        |
| Extrapolation                 | $P[X_i|X] = \frac{a_i(X)}{\sum_{k=1}^M a_k(X)}$                                     | Novel test stimulus X activates input nodes associated with trained stimuli.                                                           |
|                               | $E[Y|X_i] = m(X_i) + \frac{m(X_{i+1})-m(X_{i-1})}{X_{i+1}-X_{i-1}} \cdot [X - X_i]$ | Slope value computed from nearest training instances and then added to the response associated with the nearest training instance,m(x) |

@@

Following the procedure used by Mcdaniel et al. (2009), we will assess the ability of both ALM and EXAM to account for the empirical data when fitting the models to 1) only the training data, and 2) both training and testing data. Models will be fit directly to the trial by trial data of each individual participants, both by minimizing the root-mean squared deviation (RMSE), and by maximizing log likelihood. Because ALM has been shown to do poorly at accounting for human patterns extrapolation (DeLosh et al., 1997), we will also fit the extended EXAM version of the model, which operates identically to ALM during training, but includes a linear extrapolation mechanism for generating novel responses during testing.

<details class="code-fold">

<summary>Code</summary>

```{r}
almParamsV <- cbind(Model="ALM Test Only",pluck(a_te_v, "Fit"), pluck(a_te_v, "test") %>% summarise(Test_RMSE=RMSE(y,pred)) ) |>
  rbind(cbind(Model="ALM Test & Train", pluck(a_tetr_v,"Fit"), pluck(a_tetr_v, "test") %>% summarise(Test_RMSE=RMSE(y,pred)))) |>
  rbind(cbind(Model="ALM Train Only", pluck(a_tr_v, "Fit"), pluck(a_tr_v, "test") %>% summarise(Test_RMSE=RMSE(y,pred)))) |>
  mutate(across(where(is.numeric), \(x) round(x, 3)))

@@

hybridParamsC <-cbind(Model="Hybrid Test Only",pluck(hybrid_te_c, "Fit"), pluck(hybrid_te_c, "test") %>% summarise(Test_RMSE=RMSE(y,pred))) |>
  rbind(cbind(Model="Hybrid Test & Train", pluck(hybrid_tetr_c,"Fit"), pluck(hybrid_tetr_c, "test") %>% summarise(Test_RMSE=RMSE(y,pred)))) |>
  rbind(cbind(Model="Hybrid Train Only", pluck(hybrid_tr_c, "Fit"), pluck(hybrid_tr_c, "test") %>% summarise(Test_RMSE=RMSE(y,pred)))) |>
  mutate(across(where(is.numeric), \(x) round(x, 3)))
```

</details>

<details class="code-fold">

<summary>Code</summary>

```{r}
pander(almParamsV, caption="ALM"); pander(examParamsV, caption="EXAM"); pander(hybridParamsV,caption="Hybrid") 
```

</details>

|      Model       |   c   |  lr  | Value | Test_RMSE |
|:----------------:|:-----:|:----:|:-----:|:---------:|
|  ALM Test Only   | 0.134 | 2.03 | 95.46 |   95.46   |
| ALM Test & Train | 0.067 | 0.1  | 247.3 |   106.5   |
|  ALM Train Only  | 0.047 | 0.08 | 139.2 |    109    |

ALM

|       Model       |   c   |  lr  | Value | Test_RMSE |
|:-----------------:|:-----:|:----:|:-----:|:---------:|
|  EXAM Test Only   | 0.409 | 1.91 | 45.84 |   45.84   |
| EXAM Test & Train | 0.074 | 0.1  | 201.4 |   60.18   |
|  EXAM Train Only  | 0.047 | 0.08 | 139.2 |   65.31   |

EXAM

|        Model        |   c   |  lr   |   w   | Value | Test_RMSE |
|:-------------------:|:-----:|:-----:|:-----:|:-----:|:---------:|
|  Hybrid Test Only   | 0.395 | 2.017 | 0.643 | 33.88 |   33.88   |
| Hybrid Test & Train | 0.134 | 2.017 | 0.786 | 197.2 |   46.51   |
|  Hybrid Train Only  | 0.042 | 0.067 |   0   | 139.2 |   110.3   |

Hybrid

<details class="code-fold">

<summary>Code</summary>

```{r}
pander(almParamsC, caption="ALM"); pander(examParamsC, caption="EXAM"); pander(hybridParamsC,caption="Hybrid")
```

</details>

|      Model       |   c   |  lr  | Value | Test_RMSE |
|:----------------:|:-----:|:----:|:-----:|:---------:|
|  ALM Test Only   |   0   | 0.1  | 309.5 |   347.8   |
| ALM Test & Train | 0.047 | 0.08 |  361  |   328.5   |
|  ALM Train Only  | 0.06  | 0.1  | 32.44 |    329    |

ALM

|       Model       |   c   |  lr   | Value | Test_RMSE |
|:-----------------:|:-----:|:-----:|:-----:|:---------:|
|  EXAM Test Only   | 0.007 | 1.327 | 127.3 |   127.3   |
| EXAM Test & Train | 0.081 | 0.161 | 194.6 |    132    |
|  EXAM Train Only  | 0.06  |  0.1  | 32.44 |   199.8   |

EXAM

|        Model        |   c   |  lr   |  w  | Value | Test_RMSE |
|:-------------------:|:-----:|:-----:|:---:|:-----:|:---------:|
|  Hybrid Test Only   | 0.008 | 1.58  |  1  | 127.3 |   127.3   |
| Hybrid Test & Train | 0.067 | 0.134 |  1  | 194.5 |   136.4   |
|  Hybrid Train Only  | 0.042 | 0.067 |  0  | 31.5  |   330.3   |

Hybrid

## Varied Testing Predictions

<details class="code-fold">

<summary>Code</summary>

```{r}
####

@@

vte/vtetr/vtr
```

</details>

![](htw_exam.markdown_strict_files/figure-markdown_strict/fig-model-preds-varied-1.jpeg)

## Varied Testing

<details class="code-fold">

<summary>Code</summary>

```{r}
tvte<- pluck(a_te_v, "test") |> rename(ALM=pred,Observed=y) %>% 
  cbind(.,EXAM=pluck(ex_te_v, "test") |> pull(pred)) %>%
  cbind(., Hybrid=pluck(hybrid_te_v, "test") |> pull(pred))

@@

pander(tvte, caption="Varied fit to test only")
pander(tvtetr,caption="Varied fit to train and test")
pander(tvtr,caption="Varied fit to train only")
```

</details>

|  x   | Observed | ALM  | EXAM  | Hybrid |
|:----:|:--------:|:----:|:-----:|:------:|
| 100  |   663    | 675  | 715.6 | 708.5  |
| 350  |  764.2   | 675  | 817.2 | 792.1  |
| 600  |  883.9   | 675  | 895.1 | 874.7  |
| 800  |   1083   | 1078 | 1000  |  1091  |
| 1000 |   1196   | 1202 | 1199  |  1204  |
| 1200 |   1283   | 1230 | 1282  |  1221  |

Varied fit to test only

|  x   | Observed | ALM  | EXAM  | Hybrid |
|:----:|:--------:|:----:|:-----:|:------:|
| 100  |   663    | 675  | 715.6 | 707.3  |
| 350  |  764.2   | 675  | 817.2 |  788   |
| 600  |  883.9   | 675  |  902  | 851.5  |
| 800  |   1083   | 1000 | 1000  |  1004  |
| 1000 |   1196   | 1163 | 1165  |  1196  |
| 1200 |   1283   | 1191 | 1194  |  1227  |

Varied fit to train and test

|  x   | Observed |  ALM  | EXAM  | Hybrid |
|:----:|:--------:|:-----:|:-----:|:------:|
| 100  |   663    |  675  | 715.6 |  675   |
| 350  |  764.2   |  675  | 817.1 |  675   |
| 600  |  883.9   |  675  | 904.8 |  675   |
| 800  |   1083   | 999.8 | 999.8 | 999.3  |
| 1000 |   1196   | 1150  | 1150  |  1143  |
| 1200 |   1283   | 1180  | 1180  |  1176  |

Varied fit to train only

## Constant Testing Predictions

<details class="code-fold">

<summary>Code</summary>

```{r}
####

@@

cte/ctetr/ctr
```

</details>

![](htw_exam.markdown_strict_files/figure-markdown_strict/fig-model-preds-constant-1.jpeg)

<details class="code-fold">

<summary>Code</summary>

```{r}
tcte<- pluck(a_te_c, "test") |> rename(ALM=pred,Observed=y) %>% 
  cbind(.,EXAM=pluck(ex0_te_c, "test") |> pull(pred)) %>%
  cbind(., Hybrid=pluck(hybrid_te_c, "test") |> pull(pred))

@@

pander(tcte, caption="Constant fit to test only")
pander(tctetr,caption="Constant fit to train and test")
pander(tctr,caption="Constant fit to train only")
```

</details>

|  x   | Observed | ALM | EXAM  | Hybrid |
|:----:|:--------:|:---:|:-----:|:------:|
| 100  |  526.7   | 675 | 716.9 | 716.8  |
| 350  |  666.3   | 675 | 821.7 | 821.3  |
| 600  |  779.6   | 675 | 926.6 | 925.7  |
| 800  |   980    | 675 | 1010  |  1009  |
| 1000 |   1163   | 675 | 1094  |  1093  |
| 1200 |   1277   | 675 | 1178  |  1176  |

Constant fit to test only

|  x   | Observed |  ALM  | EXAM  | Hybrid |
|:----:|:--------:|:-----:|:-----:|:------:|
| 100  |  526.7   |  675  | 712.4 | 710.6  |
| 350  |  666.3   |  675  | 806.1 | 799.6  |
| 600  |  779.6   |  675  | 899.7 | 888.6  |
| 800  |   980    | 858.9 | 974.6 | 959.8  |
| 1000 |   1163   |  675  | 1049  |  1031  |
| 1200 |   1277   |  675  | 1124  |  1102  |

Constant fit to train and test

|  x   | Observed | ALM | EXAM | Hybrid |
|:----:|:--------:|:---:|:----:|:------:|
| 100  |  526.7   | 675 | 697  |  675   |
| 350  |  666.3   | 675 | 752  |  675   |
| 600  |  779.6   | 675 | 807  |  675   |
| 800  |   980    | 851 | 851  | 832.7  |
| 1000 |   1163   | 675 | 895  |  675   |
| 1200 |   1277   | 675 | 939  |  675   |

Constant fit to train only

<details class="code-fold">

<summary>Code</summary>

```{r}
pluck(a_te_v, "train") |> pivot_longer(y:almResp, names_to="Resp", values_to = "vx") |> 
  mutate(dev=x-vx,abs_dev=abs(x-vx)) |>
  learn_curve_plot(tr, vx, Resp,facet_var=x, groupVec=Resp,nbins=8)

@@

list(a_tr_v, a_te_v,a_tetr_v) |> map( ~{pluck(.x, "train") |> pivot_longer(y:almResp, names_to="Resp", values_to = "vx") |> mutate(dev=x-vx,abs_dev=abs(x-vx)) |>
  ungroup() %>%
  gather(key = "variable", value = "y_value", dev, abs_dev, vx) %>%
  group_by(variable) %>%
  group_map(~ learn_curve_plot(.x, x_var = tr, y_var = y_value, color_var = Resp, facet_var = x, groupVec = Resp, nbins = 8, y_label = .y$variable), .keep = TRUE) })
```

</details>

# EXAM fit learning curves

<details class="code-fold">

<summary>Code</summary>

```{r}
pluck(ex_te_v, "train") |> pivot_longer(y:almResp, names_to="Resp", values_to = "vx") |> 
  mutate(dev=x-vx,abs_dev=abs(x-vx)) |>
  learn_curve_plot(tr, vx, Resp,facet_var=x, groupVec=Resp,nbins=8)

pluck(ex_te_v, "train") |> pivot_longer(y:almResp, names_to="Resp", values_to = "vx") |> 
  mutate(dev=x-vx,abs_dev=abs(x-vx)) |>
  ungroup() %>%
  gather(key = "variable", value = "y_value", dev, abs_dev, vx) %>%
  group_by(variable) %>%
  group_map(~ learn_curve_plot(.x, x_var = tr, y_var = y_value, color_var = Resp, facet_var = x, groupVec = Resp, nbins = 8, y_label = .y$variable), .keep = TRUE)
```

</details>

<details class="code-fold">

<summary>Code</summary>

```{r}
optimize_params_weighted_individual <- function(ds, c_values, lr_values, weight_exam_values, input.layer, output.layer) {
    all_results <- list()

@@

</details>

DeLosh, E. L., McDaniel, M. A., & Busemeyer, J. R. (1997). Extrapolation: The Sine Qua Non for Abstraction in Function Learning. *Journal of Experimental Psychology: Learning, Memory, and Cognition*, *23*(4), 19. <https://doi.org/10.1037/0278-7393.23.4.968>

Kruschke, J. K. (1992). ALCOVE: An exemplar-based connectionist model of Category Learning. *Psychological Review*, *99*(1). <https://doi.org/10.1037/0033-295X.99.1.22>

Mcdaniel, M. A., Dimperio, E., Griego, J. A., & Busemeyer, J. R. (2009). Predicting transfer performance: A comparison of competing function learning models. *Journal of Experimental Psychology. Learning, Memory, and Cognition*, *35*, 173--195. <https://doi.org/10.1037/a0013982>
